SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2018-12-07 abs.tex
Mostly related to images, methodology, typos etc
Small changes throughout the paper

  In this paper, we introduce Perceptron-based Prefetch Filtering
  (PPF) as a way increase the coverage of the prefetches generated by
  a baseline prefetcher without negatively impacting accuracy.  PPF
  enables more aggressive tuning of a given baseline prefetcher,
  leading to increased coverage by filtering out the growing numbers
  of inaccurate prefetches such an aggressive tuning implies.  We also
  explore a range of features to use to train PPF's perceptron layer
  to identify inaccurate prefetches.  PPF improves performance on a
  memory-intensive subset of the SPEC CPU 2017 benchmarks by 6.84\%
  for a single-core configuration, and by 11.9\% for a 4-core
  configuration, compared to the baseline prefetcher alone.  We also
  show that performance continues to scale as the number of cores
  sharing a last level cache increases.

>>>>

In this paper, we introduce Perceptron-based Prefetch Filtering
(PPF) as a way increase the coverage of the prefetches generated by
a baseline prefetcher without negatively impacting accuracy. PPF
enables more aggressive tuning of a given baseline prefetcher,
leading to increased coverage by filtering out the growing numbers
of inaccurate prefetches such an aggressive tuning implies. We also
explore a range of features to use to train PPF's perceptron layer
to identify inaccurate prefetches. PPF improves performance on a
memory-intensive subset of the SPEC CPU 2017 benchmarks by 3.78\%
for a single-core configuration, and by 11.4\% for a 4-core
configuration, compared to the baseline prefetcher alone. We also
show that performance continues to scale as the number of cores
sharing a last level cache increases.

### 2018-12-07 back.tex
Small changes throughout the paper

\section{Motivation and Prior Work}
\label{Background}

In this section we discuss the most closely related work to our proposed
technique. See Section~\ref{related} for other relevant work.

The idea of prefetching begins with Jouppi's \textit{Instruction Stream
Buffers}~\cite{ISB}. Early prefetchers detected stride access patterns in order to
predict future memory requests~\cite{Smith,Baer,Stride}. Modern prefetching
mechanisms are more sophisticated as they look into past memory
behavior~\cite{Address_Correlated,AMPM},
locality~\cite{Spatial_Pattern,SMS,Temporal_Instruction_Fetch,Off_Chip,STMS,SMS_JILP},
control-flow speculation~\cite{BFetch,MTBFetch}, and many other aspects to
detect complex access patterns in modern applications.

\subsection{Lookahead-based Prefetchers}

%% Simple stride prefetching techniques only detect sequences of addresses that differ by a constant value and fail to capture diverse memory access patterns. 
Lookahead prefetchers can learn complicated patterns by collecting histories of
observed data access patterns.
%EB: Didn't really understand this: 
%% "and correlating these with the strides, by considering each new page in a vacuum."
Kim {\em et. al.} proposed
SPP~\cite{SPP}, a confidence-based lookahead prefetcher. SPP creates a
signature associated to a memory request by compressing the history of
accesses. By correlating the signature with future likely delta patterns, SPP
learn both simple and complicated memory access patterns quickly. Our proposed
technique builds upon SPP. Thus, we describe SPP in more detail.

\subsection{Baseline Prefetcher: The Signature Path Prefetcher}
\label{Background-SPP}

While the basic idea of perceptron based prefetch filtering is applicable to
any look-ahead prefetcher, we develop a practical implementation of the idea
using SPP as our baseline. Here we describe the basic architecture of SPP.\\

\noindent \textbf{Signature Table:} The Signature Table keeps track of 256 most recently
accessed pages. It is meant to capture memory access patterns within a page
boundary. SPP indexes into an entry of the Signature Table using the page
number. For each entry corresponding to a page, the table stores a `last
block offset' and an `old signature'. Last block offset is the block offset
of the last memory access of that given page. The block offset is calculated
with respect to the page boundary. The signature is a 12-bit compressed
representation of the past few memory accesses for that page. The signature
is calculated as: $$New Signature = (\,Old Signature << 3 bits\,) \;\;XOR\;\;
(\,Delta\,)$$ Delta is the numerical difference between the block offset of
the current and the previous memory access. In case a matching page entry is
found, the stored signature retrieved and used to index into the Pattern
Table. This process is illustrated by figure \ref{fig:spp_update}.\\

\noindent \textbf{Pattern Table:} The Pattern Table is indexed by the signature
generated from the Signature Table. Pattern Table holds predicted delta
patterns and their confidence estimates. Each entry indexed by the signature
holds up to 4 unique delta predictions. This is implemented by making the
Pattern Table 4-way associative.\\

@@

%% NOTE: Can we do away with this example? 
%% If it looks like we are writing too much about SPP
%% EDIT: Decided to reorganize and remove this for now.
%% 	Consider the case that incoming page number 10 with a block offset 3
%% 	finds a match in the ST. The retrieved pattern signature is 0x30 and
%% 	the Last Offset is 1. Since now there is the Last Block Offset (1),
%% 	Incoming Block Offset (3), Old Signature (0x30), and New Signature
%% 	calculated as per above equation (0x182), SPP can infer
%% 	non-speculatively that the given pattern of memory accesses (as
%% 	captured in the Old Signature) leads to the particular Delta. In
%% 	general, Delta is defined as the difference between the prefetch
%% 	suggestion block and the initial block which triggered the prefetch.
%% 	In this case, since SPP is in learning phase, it is defined as the
%% 	difference between the Incoming Block Offset and the Last Block Offset
%% 	(+2 in this case). This, in turn generates the new memory pattern
%% 	(New Signature). This newly learned signature pattern and the delta
%% 	is stored in the Pattern Table.

\noindent \textbf{Prefetch Table:} The Prefetch Table is a 1024 entry 1-way associative
table that keeps a record of last few entries prefetched. This proves useful
for updating the prefetcher states if a tracked prefetch leads to a demand hit
or a cache eviction. \textit{Note:} The original paper refers to this as the
Prefetch Filter but since in our context filter refers to the perceptron
filter, we will be calling this structure as the Prefetch Table to avoid any
confusion.\\

\noindent \textbf{Lookahead Prefetching:} On each trigger, SPP goes down the program
speculation path using its own prefetch suggestion. Using current prefetch as
the baseline, it re-accesses the Pattern Table to generate further prefetches.
It repeats the cycle of accessing Pattern Table and updating the signature
based on highest confidence prefetch from the last iteration. The iteration
counter on which SPP manages to predict prefetch entries in the lookahead
manner is characterized as its `depth'. While doing so, SPP also keeps
compounding the confidence in each depth. Thus as depth increases, overall
confidence keeps decreasing.\\

\noindent \textbf{Confidence Tracking}: The Pattern Table keeps a count of hits to each
signature through a counter C\textsubscript{sig}. The number of hits for a
given delta per signature are tracked using a counter C\textsubscript{delta}.
The confidence for a given delta is approximated through C\textsubscript{d} =
C\textsubscript{delta} / C\textsubscript{sig}. When SPP enters into a
lookahead mode, the path confidence P\textsubscript{d} is given as:
$$P\textsubscript{d} \;=\; \alpha  \;.\;  C\textsubscript{d}  \;.\;
P\textsubscript{d-1}$$ Here $\alpha$ represents the global accuracy,
calculated as the ratio of the number of prefetches which led to a demand hit
to the number of prefetches recommended in total. The range of $\alpha$ is [0,1].
$D$ is the lookahead depth. For $d = 1$, when SPP is in
non-speculative mode, P\textsubscript{0} can be thought of as 1. 
The final P\textsubscript{d} is thresholded against prefetch threshold 
(T\textsubscript{p}) to reject the low confidence suggestions and 
then against a numerically bigger fill threshold (T\textsubscript{f}) to 
decide whether the prefetch should be sent to L2 Cache 
(high confidence prefetch) or Last Level Cache (low confidence prefetch).
The two thresholds were empirically set to 25 and 90 respectively, 
on the scale of 0 to 100.

\begin{figure}
  \begin{center}
  \includegraphics[width=\columnwidth]{SPP_Prefetch_Description}
    \label{fig:spp_strcture}
  \caption{SPP Architecture}
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=\columnwidth]{SPP_Update_Description}
  \label{fig:spp_update}
  \caption{SPP Data-path Flow}
  \end{center}
\end{figure}

@@

As was noted in Figure~\ref{Fig:Motivation}, an aggressive lookahead 
prefetching if done without any accuracy check, can harm the performance 
of the system. In this given case, the effective performance gained
by the original prefetcher is lost by almost 9\% by the aggressive version 
of the same prefetcher. Most modern prefetchers are getting increasingly 
aggressive as that enables them to capture the complex memory access patterns 
seen in pointer-chasing applications. Thus, we need a mechanism that is 
orthogonal to the underlying prefetching scheme and can be used
to prune out the useful prefetcher from the useless ones.

>>>>

\section{Motivation}
\label{Background}

In this section we discuss the most closely related work to our proposed technique. 
The idea of prefetching begins with Jouppi's \textit{Instruction Stream
Buffers}~\cite{ISB}. Early prefetchers detected stride access patterns in order to
predict future memory requests~\cite{Smith,Baer,Stride}. Modern prefetching
mechanisms are more sophisticated as they look into past memory
behavior~\cite{Address_Correlated,AMPM},
locality~\cite{Spatial_Pattern,SMS,Temporal_Instruction_Fetch,Off_Chip,STMS,SMS_JILP},
control-flow speculation~\cite{BFetch,MTBFetch}, and other other aspects to
detect complex memory access patterns.
See Section~\ref{related} for other relevant work.

% [EB:] Removing this section title and moving relevant text to next section
%       We weren't talking about LA prefetchers here anyway, just SPP
% \subsection{Lookahead-based Prefetchers}
%% Simple stride prefetching techniques only detect sequences of addresses that differ by a constant value and fail to capture diverse memory access patterns. 
%Lookahead prefetchers can learn complicated patterns by collecting histories of observed data access patterns.
%EB: Didn't really understand this: 
%% "and correlating these with the strides, by considering each new page in a vacuum."

\subsection{Baseline Prefetcher: SPP}
\label{Background-SPP}

Kim {\em et. al.} proposed Signature Path Prefetcher (SPP)~\cite{SPP}, 
a confidence-based lookahead prefetcher. 
SPP creates a signature associated with a page address by compressing the history of 
accesses. By correlating the signature with future likely delta patterns, SPP learns 
both simple and complicated memory access patterns quickly. 
While the basic idea of perceptron based prefetch filtering is applicable to
any look-ahead prefetcher, we develop a practical implementation of the idea
using SPP as our baseline. Here we describe the basic architecture of SPP.\\
%
\noindent \textbf{Signature Table:} As shown in figure \ref{fig:spp_structure}, 
the Signature Table keeps track of 256 most recently
accessed pages. It is meant to capture memory access patterns within a page
boundary. SPP indexes into an entry of the Signature Table using the page
number. For each entry corresponding to a page, the table stores a `last
block offset' and an `old signature'. Last block offset is the block offset
of the last memory access of that given page. The block offset is calculated
with respect to the page boundary. The signature is a 12-bit compressed
representation of the past few memory accesses for that page. The signature
is calculated as: $$New Signature = (\,Old Signature << 3 bits\,) \;\;XOR\;\;
(\,Delta\,)$$ Delta is the numerical difference between the block offset of
the current and the previous memory access. In case a matching page entry is
found, the stored signature retrieved and used to index into the Pattern
Table. This process is illustrated by figure \ref{fig:spp_update}.\\
%
\noindent \textbf{Pattern Table:} The Pattern Table is indexed by the signature
generated from the Signature Table. Pattern Table holds predicted delta
patterns and their confidence estimates. Each entry indexed by the signature
holds up to 4 unique delta predictions.\\
%

@@

%% NOTE: Can we do away with this example? 
%% If it looks like we are writing too much about SPP
%% EDIT: Decided to reorganize and remove this for now.
%% 	Consider the case that incoming page number 10 with a block offset 3
%% 	finds a match in the ST. The retrieved pattern signature is 0x30 and
%% 	the Last Offset is 1. Since now there is the Last Block Offset (1),
%% 	Incoming Block Offset (3), Old Signature (0x30), and New Signature
%% 	calculated as per above equation (0x182), SPP can infer
%% 	non-speculatively that the given pattern of memory accesses (as
%% 	captured in the Old Signature) leads to the particular Delta. In
%% 	general, Delta is defined as the difference between the prefetch
%% 	suggestion block and the initial block which triggered the prefetch.
%% 	In this case, since SPP is in learning phase, it is defined as the
%% 	difference between the Incoming Block Offset and the Last Block Offset
%% 	(+2 in this case). This, in turn generates the new memory pattern
%% 	(New Signature). This newly learned signature pattern and the delta
%% 	is stored in the Pattern Table.
\noindent \textbf{Prefetch Table:} The Prefetch Table is a 1024 entry 1-way associative
table that keeps a record of last few entries prefetched. This proves useful
for updating the prefetcher states if a tracked prefetch leads to a demand hit
or a cache eviction. \textit{Note:} The original paper refers to this as the
Prefetch Filter but since in our context filter refers to the perceptron
filter, we will be calling this structure as the Prefetch Table to avoid any
confusion.\\
%
\noindent \textbf{Lookahead Prefetching:} On each trigger, SPP goes down the program
speculation path using its own prefetch suggestion. Using current prefetch as
the baseline, it re-accesses the Pattern Table to generate further prefetches.
It repeats the cycle of accessing Pattern Table and updating the signature
based on highest confidence prefetch from the last iteration. The iteration
counter on which SPP manages to predict prefetch entries in the lookahead
manner is characterized as its `depth'. While doing so, SPP also keeps
compounding the confidence in each depth. Thus as depth increases, overall
confidence keeps decreasing.\\
%
\noindent \textbf{Confidence Tracking}: The Pattern Table keeps a count of hits to each
signature through a counter C\textsubscript{sig}. The number of hits for a
given delta per signature are tracked using a counter C\textsubscript{delta}.
The confidence for a given delta is approximated through C\textsubscript{d} =
C\textsubscript{delta} / C\textsubscript{sig}. When SPP enters into a
lookahead mode, the path confidence P\textsubscript{d} is given as:
$$P\textsubscript{d} \;=\; \alpha  \;.\;  C\textsubscript{d}  \;.\;
P\textsubscript{d-1}$$ Here $\alpha$ represents the global accuracy,
calculated as the ratio of the number of prefetches which led to a demand hit
to the number of prefetches recommended in total. The range of $\alpha$ is [0,1].
$D$ is the lookahead depth. For $d = 1$, when SPP is in
non-speculative mode, P\textsubscript{0} can be thought of as 1. 
The final P\textsubscript{d} is thresholded against prefetch threshold 
(T\textsubscript{p}) to reject the low confidence suggestions and 
then against a numerically bigger fill threshold (T\textsubscript{f}) to 
decide whether the prefetch should be sent to L2 Cache 
(high confidence prefetch) or Last Level Cache (low confidence prefetch).
The two thresholds were empirically set to 25 and 90 respectively, 
on the scale of 0 to 100.

\begin{figure}
  \begin{center}
  \includegraphics[width=\columnwidth]{SPP_Prefetch_Description}
  \caption{SPP Architecture}
  \label{fig:spp_structure}
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=\columnwidth]{SPP_Update_Description}
  \caption{SPP Data-path Flow}
  \label{fig:spp_update}
  \end{center}
\end{figure}

@@

As was noted in Figure~\ref{Fig:Motivation}, an aggressive lookahead 
prefetching if done without any accuracy check, can harm the performance 
of the system. In this given case, the effective performance gained
by the original prefetcher is lost by almost 9\% by the aggressive version 
of the same prefetcher. Most modern prefetchers are getting increasingly 
aggressive as that enables them to capture the complex memory access patterns 
seen in pointer-chasing applications. Thus, we need a mechanism that is 
orthogonal to the underlying prefetching scheme and can be used
to prune out the useful prefetches from the useless ones.

### 2018-12-07 intro.tex
Mostly related to images, methodology, typos etc
Small changes throughout the paper

\begin{figure}[t]
\includegraphics[width=\columnwidth]{Motivation}
\caption{Variation of IPC, Total Prefetches and Useful Prefetches}
\label{Fig:Motivation}
\end{figure}

@@

Figure~\ref{Fig:Motivation} illustrates the above scenario in a working manner.
Here we consider a state-of-the-art lookahead prefetcher -- SPP. We keep on 
re-tuning its thresholds, each time getting a variant with an increasing lookahead 
depth coverage. The figure depicts the behavior of the prefetcher variants running 
on the trace {\tt 603.bwaves\_s-1740B}. The IPC, total number of prefetches 
suggested by the prefetcher (TOTAL\_PF) and the actual useful predictions (GOOD\_PF),
all have been normalized to the least aggressive version of the prefetcher. 
As the look-ahead depth of the prefetch suggestions increase, so do useful prefetches. 
But that comes at a cost of total prefetches increasing at an even higher rate. This leads 
to cache pollution and bandwidth contention, as is clearly visible with the reduction in 
the IPC. Similar behavior was observed in 12 other SPEC CPU 2017 simpoints.

@@

We propose Perceptron-based Prefetch Filtering (PPF) as an enhancement to
existing state-of-the-art prefetchers.  PPF works by observing the stream of
candidate prefetches generated by a prefetcher, and then rejects those that
are predicted by the online-trained neural model to be inaccurate.
The state-of-the-art prefetcher that we 
use to evaluate PPF in this paper is the Signature Path Prefetcher 
(SPP)~\cite{SPP}, however in principle, PPF could benefit any prefetcher.
In this design, PPF replaces SPP's existing confidence-based throttling mechanism,
which itself was a highly tuned feature of that prefetcher.  Because PPF is
so much more effective at rejecting inaccurate prefetches than SPP's baseline
mechanism, we are free to re-tune the rest of SPP's design around maximizing
coverage.  The result is an increase in both accuracy and coverage, and
a notable increase in performance.

@@

\item Implementing PPF filtering a state-of-the-art prefetchier, giving a
significant performance improvement compared to previous work.  PPF learns to
adapt itself to shared resource constraints, leading to further increased
performance in multi-core and bandwidth-constrained environments.

\item A methodology for determining an appropriate set of features for
prediction, regardless of the underlying prefetcher used.  More details are
explained in Section \ref{Method-Features}.

@@

In a single core configuration, PPF increases performance by 6.84\%
compared to the underlying prefetcher, SPP.  In a multi-core system running a
mixes of memory intensive SPEC CPU 2017 traces, PPF saw an improvement
of 11.9\% over SPP for a 4-core system, and 10.67\% for an 8-core system.

>>>>

\begin{figure}[t]
\includegraphics[width=\columnwidth]{Motivation}
\caption{Impact of aggressive prefetching on performance. X-asis represents increasingly 
	 aggressive prefetch lookahead depth. All the metrics have been normalized
	 to the least aggressive configuration. As can be seen, total number of prefetches increases at a
	 higher rate than the number of good prefetches, leading to IPC reduction.}
\label{Fig:Motivation}
\end{figure}

@@

Figure~\ref{Fig:Motivation} illustrates the above scenario in a working manner.
Here we consider a state-of-the-art lookahead prefetcher -- SPP. We keep on 
re-tuning its thresholds, each time getting a variant with an increasing lookahead 
depth coverage. The figure depicts the behavior of the prefetcher variants running 
on the trace {\tt 603.bwaves\_s}. The IPC, total number of prefetches 
suggested by the prefetcher (TOTAL\_PF) and the actual useful predictions (GOOD\_PF),
all have been normalized to the least aggressive version of the prefetcher. 
As the look-ahead depth of the prefetch suggestions increase, so do useful prefetches. 
But that comes at a cost of total prefetches increasing at an even higher rate. This leads 
to cache pollution and bandwidth contention, as is clearly visible with the reduction in 
the IPC. 
%%Similar behavior was observed in 12 other SPEC CPU 2017 simpoints.

@@

We propose Perceptron-based Prefetch Filtering (PPF) as an enhancement to
existing state-of-the-art prefetchers. PPF works by observing the stream of
candidate prefetches generated by a prefetcher, and then rejects those that
are predicted by the online-trained neural model to be inaccurate.
The state-of-the-art prefetcher that we 
use to evaluate PPF in this paper is the Signature Path Prefetcher 
(SPP)~\cite{SPP}, however in principle, PPF could benefit any prefetcher.
In this design, PPF replaces SPP's existing confidence-based throttling mechanism,
which itself was a highly tuned feature of that prefetcher. Because PPF is
so much more effective at rejecting inaccurate prefetches than SPP's baseline
mechanism, we are free to re-tune the rest of SPP's design around maximizing
coverage. This results in a notable increase in system performance.

@@

\item Implementing PPF filtering on a state-of-the-art prefetcher, giving a
significant performance improvement compared to previous work. PPF learns to
adapt itself to shared resource constraints, leading to further increased
performance in multi-core and small LLC environments.

\item A methodology to determine an appropriate set of features for
prediction, regardless of the underlying prefetcher used. More details are
explained in Section \ref{Method-Features}.

@@

In a single core configuration, PPF increases performance by 3.78\%
compared to the underlying prefetcher, SPP. In a multi-core system running a
mixes of memory intensive SPEC CPU 2017 traces, PPF saw an improvement
of 11.4\% over SPP for a 4-core system, and 9.65\% for an 8-core system.

### 2018-12-07 results.tex
Small changes throughout the paper

% djimenez: is this geometric mean? if so, say so.
% [EB] Resolved
On the full SPEC CPU 2017 suite, PPF improves the geometric mean IPC of 
the baseline by \textbf{15.24\%}, which is \textbf{2.27\%} better 
than the next best prefetcher -- SPP.
\newline

\begin{figure}[h]
\includegraphics[width=\columnwidth]{Coverage}
\caption{Fraction of Cache Misses Covered}
\label{Fig:Coverage}
\end{figure}

% djimenez: this is a weird way to make a header for a section. use \paragraph or \subsection

\noindent \textbf{COVERAGE}
\newline
Prefetcher coverage is defined as the ratio of the number of misses avoided
through prefetching to the number of misses with no prefetching.

@@

\subsection{Multi-core Results}
\label{Results-Multi}
In this section, we demonstrate the improvement achieved by PPF for a mix of
multi-programmed workloads.
\newline

\noindent \textbf{4-CORE ENVIRONMENT}
\newline
Figure~\ref{Fig:4Core_SPEC2017} shows a comparison of speedups obtained on
4-core mixes of a memory intensive subset SPEC CPU 2017. We plot all 4
prefetchers, normalized to the baseline. The workloads have been sorted in
increasing order of the speedup. PPF offers a speedup of \textbf{51.2\%} on
these traces, and improvement of \textbf{11.4\%} over the baseline SPP,
\textbf{9.7\%} over the next DA-AMPM, and \textbf{16.9\%} over BOP.

On a different set of fully random SPEC CPU 2017 4-core mixes (not illustrated
for space reasons), PPF provides an IPC speedup of \textbf{26.07}\% over the
baseline, which is an improvement of \textbf{5.6}\% over SPP.

%\begin{figure*}[ht]
%\includegraphics[width=\textwidth]{8Core_SPEC2017}
%\caption{Normalized Speedup for 8-core SPEC CPU 2017 Workloads}
%\label{Fig:8Core_SPEC2017}
%\end{figure*}

\begin{figure}[ht]
\includegraphics[width=2.75in]{8Core_SPEC2017}
\caption{Speedup for 8-core SPEC CPU 2017}
\label{Fig:8Core_SPEC2017}
\end{figure}

\noindent \textbf{8-CORE ENVIRONMENT}
\newline
The sorted comparison of speedups on the memory intensive 8-core mixes is
shown in Figure~\ref{Fig:8Core_SPEC2017}. PPF improves baseline performance
by \textbf{37.6\%}, an improvement of \textbf{9.7\%} over SPP. For a random
set of SPEC CPU 2017 mixes (not illustrated for space reasons), PPF improves
performance by \textbf{23.4\%} over the baseline, corresponding to
\textbf{4.6\%} over SPP. This increased improvement achieved by PPF over the
base engine SPP in a multi-core environment is expected as PPF has a very
accurate filter, it eliminates useless prefetches before they can cause
pollution in the shared LLC.

BOP offers a better improvement than SPP for the memory intensive mixes. This
superiority can be attributed to BOP's inherent aggressive nature. DA-AMPM is
also ahead of SPP in both the mixes. Interestingly, in all these cases, PPF
consistently outperforms the best performing prefetcher.

@@

\begin{figure}[ht]
\includegraphics[width=\columnwidth]{SPEC2006}
\caption{SPEC CPU 2006 Single-Core IPC Speedup}
\label{Fig:SPEC2006_1core}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=\columnwidth,]{CloudSuite}
\caption{IPC Speedup for Multi-core CloudSuite Workloads}
\label{Fig:CloudSuite}
\end{figure}

@@

% djimenez: cite cloudsuite here? do we have a reference?
% [EB]: Resolved. Cited "Clearing the clouds: A study of emerging 
%        scale-out workloads on modern hardware" in methodology

Here we demonstrate the robustness of PPF by testing it on different
benchmarks: SPEC CPU 2006 and CloudSuite.

% djimenez: is the improvement over BOP and DA-AMPM exactly the same 9.86%
% here? that's weird.
% [EB] Resolved. Increased precision of values. But yes, BOP / DA-AMPM 
% have really close numbers for SPEC 2006

>>>>

% djimenez: is this geometric mean? if so, say so.
% [EB] Resolved
On the full SPEC CPU 2017 suite, PPF improves the geometric mean IPC of 
the baseline by \textbf{15.24\%}, which is \textbf{2.27\%} better 
than the next best prefetcher -- SPP.\\ \\
%
\begin{figure}[h]
\includegraphics[width=\columnwidth]{Coverage}
\caption{Fraction of Cache Misses Covered}
\label{Fig:Coverage}
\end{figure}
%
% djimenez: this is a weird way to make a header for a section. use \paragraph or \subsection
\noindent \textbf{Coverage:}
Prefetcher coverage is defined as the ratio of the number of misses avoided
through prefetching to the number of misses with no prefetching.

@@

\subsection{Multi-core Results}
\label{Results-Multi}
In this section, we demonstrate the improvement achieved by PPF for a mix of
multi-programmed workloads.\\ \\
%
\noindent \textbf{4-Core Environment:}
Figure~\ref{Fig:4Core_SPEC2017} shows a comparison of speedups obtained on
4-core mixes of a memory intensive subset SPEC CPU 2017. We plot all 4
prefetchers, normalized to the baseline. The workloads have been sorted in
increasing order of the speedup. PPF offers a speedup of \textbf{51.2\%} on
these traces, and improvement of \textbf{11.4\%} over the baseline SPP,
\textbf{9.7\%} over the next DA-AMPM, and \textbf{16.9\%} over BOP.
On a different set of fully random SPEC CPU 2017 4-core mixes (not illustrated
for space reasons), PPF provides an IPC speedup of \textbf{26.07}\% over the
baseline, which is an improvement of \textbf{5.6}\% over SPP.\\ \\
%
\begin{figure}[ht]
\includegraphics[width=2.75in]{8Core_SPEC2017}
\caption{Speedup for 8-core SPEC CPU 2017}
\label{Fig:8Core_SPEC2017}
\end{figure}
%
\noindent \textbf{8-Core Environment:}
The sorted comparison of speedups on the memory intensive 8-core mixes is
shown in Figure~\ref{Fig:8Core_SPEC2017}. PPF improves baseline performance
by \textbf{37.6\%}, an improvement of \textbf{9.7\%} over SPP. For a random
set of SPEC CPU 2017 mixes (not illustrated for space reasons), PPF improves
performance by \textbf{23.4\%} over the baseline, corresponding to
\textbf{4.6\%} over SPP. This increased improvement achieved by PPF over the
base engine SPP in a multi-core environment is expected as PPF has a very
accurate filter, it eliminates useless prefetches before they can cause
pollution in the shared LLC.
BOP offers a better improvement than SPP for the memory intensive mixes. This
superiority can be attributed to BOP's inherent aggressive nature. DA-AMPM is
also ahead of SPP in both the mixes. Interestingly, in all these cases, PPF
consistently outperforms the best performing prefetcher.

@@

\begin{figure}[ht]
\includegraphics[width=0.8\columnwidth,height=4cm,keepaspectratio]{SPEC2006}
\caption{SPEC CPU 2006 Single-Core IPC Speedup}
\label{Fig:SPEC2006_1core}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=0.9\columnwidth,height=3.5cm,keepaspectratio]{CloudSuite}
\caption{IPC Speedup for CloudSuite Workloads}
\label{Fig:CloudSuite}
\end{figure}

%% \begin{figure}[ht]
%%   \centering
%%   \begin{subfigure}{0.5\columnwidth}
%%     \centering
%%     \includegraphics[width=0.45\columnwidth]{CloudSuite}
%%     \caption{CloudSuite Workloads}
%%   \end{subfigure}
%%   %
%%   \begin{subfigure}{0.5\columnwidth}
%%     \centering
%%     \includegraphics[width=0.45\columnwidth]{SPEC2006}
%%     \caption{Single Core SPEC CPU 2006}
%%   \end{subfigure}
%%   \caption{Performance with Unseen Benchmarks}
%%   \label{Fig:CrossVal}
%% \end{figure}

@@

% djimenez: cite cloudsuite here? do we have a reference?
% [EB]: Resolved. Cited "Clearing the clouds: A study of emerging 
%        scale-out workloads on modern hardware" in methodology
%
% Here we demonstrate the robustness of PPF by testing it on different
% benchmarks: SPEC CPU 2006 and CloudSuite.
%
% djimenez: is the improvement over BOP and DA-AMPM exactly the same 9.86%
% here? that's weird.
% [EB] Resolved. Increased precision of values. But yes, BOP / DA-AMPM 
% have really close numbers for SPEC 2006
